### 2021-04-13 README.Rmd
updated vignette draft
cleaning up one-sample vignette
cleaning up one-sample and starting two-sample vignette

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Build Status](https://travis-ci.com/zabore/ppseq.svg?branch=main)](https://travis-ci.com/zabore/ppseq)
[![codecov](https://codecov.io/gh/zabore/ppseq/branch/master/graph/badge.svg)](https://codecov.io/gh/zabore/ppseq)
[![CRAN status](https://www.r-pkg.org/badges/version/ppseq)](https://CRAN.R-project.org/package=ppseq)
<!-- badges: end -->

The goal of ppseq is to ...

@@

``` r
remotes::install_github("zabore/ppseq")
```

## Example

This is a basic example which shows you how to solve a common problem:

``` r
library(ppseq)
## basic example code
```

>>>>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Build Status](https://travis-ci.com/zabore/ppseq.svg?branch=main)](https://travis-ci.com/zabore/ppseq) [![CRAN status](https://www.r-pkg.org/badges/version/ppseq)](https://CRAN.R-project.org/package=ppseq)
[![Codecov test coverage](https://codecov.io/gh/zabore/ppseq/branch/main/graph/badge.svg)](https://codecov.io/gh/zabore/ppseq?branch=main)
<!-- badges: end -->

The goal of ppseq is to provide functions that aid in designing clinical trials with sequential posterior probability monitoring incorporated.

@@

```r
remotes::install_github("zabore/ppseq")
```
